%---------------------------------------------------------------------
%
%                          Capítulo 2
%
%---------------------------------------------------------------------
\setlength{\parskip}{10pt}
\chapter{Introduction}

\begin{resumen}
	In this chapter we are going to make an introduction to the work that we are going to present.
	First, section 2.1 will explain what the work consists of. Then, section 2.2 will discuss the main difficulties we have faced and the decisions that have been taken to address them. Finally, section 2.3 will present the structure of the work.

\end{resumen}

%------------------------------------------------------------------
\section{Motivation}
%-------------------------------------------------------------------
\label{cap2:sec:motivacion}

At present, thanks to the Internet, we live surrounded by information. We have easy and fast access to all the information we need through various channels: blogs, social networks, websites, forums ... Even if we do not look for information, it just comes to us due to the nature of the network. Having a lot of information about the environment that surrounds us is a great advantage since it allows us to adapt to it but it involves a new challenge: the complicated thing is not to obtain the information but to be able to interpret all the information we receive from countless sources and keep that really is useful to us For this we really do not have any tool, we can only rely on our capacity of textual analysis to understand what a text says and how it says it in order to give it the importance and meaning it should have for us.

For an adult with a good knowledge of their environment can be easy to carry out an automatic analysis process that allows you to interpret all the information with which it is throughout a day, but what happens if someone does not have the necessary capabilities for it? For example, the lack of cognitive empathy suffered by people with Autism Spectrum Disorders (ASD) can lead them to misinterpret a text since not understanding the context or the tone of it can greatly alter its meaning, especially if it is a personal blog or a post on social networks. These difficulties when interpreting a text generate confusion and misunderstandings preventing people with this disability access to information on equal terms. It is necessary to develop tools that allow digital inclusion to these people.
 
	
%------------------------------------------------------------------
\section{Goals}
%-------------------------------------------------------------------
\label{cap2:sec:objetivos}

The main objective of this work is to implement a series of web services that automatically detect the degree of affective load that a text has. It will be measured, specifically, the degree of intensity that presents for the five basic emotional categories with which we have decided to work: sadness, fear, joy, anger and disgust. For this we will have an emotional dictionary that will have a series of words accompanied by its lexeme and five values ??from one to five (one for each emotional category). We will develop services to analyze words, phrases and texts making explicit the affective content in each case: showing the emotional degrees and / or the majority emotion. Once the services are developed, we will integrate them into an API to make them accessible to everyone who needs them. In addition, we will create a web application so that they can be used by any user in a simple way. This website will allow you to enter text and display the results graphically, using emoticons and colors to make explicit the emotional categories contained in the text entered and marking the words that we consider emotional because they can be found in our dictionary.

This work is an opportunity to apply all the knowledge acquired during the race to a large project with real impact. We will follow an agile methodology that allows us to work as a multidisciplinary team in which we can all learn as much as possible while developing a tool that helps anyone who finds difficulties when interpreting the emotional content of a text.
%------------------------------------------------------------------
\section{Memoir Structure}
%-------------------------------------------------------------------
\label{cap2:sec:estructura}

	The memoir of this work will contain a total of twelve chapters, including this introductory one. Next, the content of each of the chapters will be detailed.
	
	
	\begin{itemize}
		\item The \textbf{chapter one} is the original introduction in Spanish.
		
		\item In the \textbf{chapter three} the most important aspects of affective computing will be presented. In addition, web services, the Scrum methodology and continuous integration will be introduced; technology and methodologies that will be used throughout the work.
		
		\item In the \textbf{chapter four} will describe the tools that we will use throughout the work: the basic tools such as the GitHub repository, the emotional dictionary with which we will do the analysis, the tool that will allow us to develop web services (Django) , Trello that will help us to follow the Scrum methodology, the tools that we will use to carry out the tests and the continuous integration (Doctest and Jenkins) and the tools that we will use for the lemmatization of the words and their filtering (SpaCy and PyStemmer).
		
		\item In the \textbf{chapter five} will be detailed each one of the web services developed during the work, dedicated both to the analysis of words as well as to sentences or texts.
		
		\item The \textbf{chapter six} details the web application that we have developed using the web services as well as the process of designing its interface and its development.
		
		\item In the \textbf{chapter seven} appear the results obtained after the evaluations we made of the application: a general evaluation of the method and two evaluations of the application with end users and experts, a preliminary and a final one.
		
		\item The \textbf{chapter eight} shows the methodology we use throughout the project and comments on each of the sprints carried out.
		
		\item The \textbf{chapter nine} explains the way in which the knowledge we have acquired has been applied throughout the grade, commenting on how the different subjects have helped us.

		\item The \textbf{chapter ten} contains a summary of the work done individually by each one of us.
		
		\item In the \textbf{chapter eleven} the main conclusions of this TFG are presented as well as the ideas that have arisen throughout the development or evaluation and that can be carried out in the future using the work we have done.
		
		\item The \textbf{chapter twelve} is a translation of the chapter "Conclusions and Future Work", the eleventh, into English.
		
	\end{itemize}
	

% Variable local para emacs, para  que encuentre el fichero maestro de
% compilación y funcionen mejor algunas teclas rápidas de AucTeX
%%%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Tesis.tex"
%%% End:
